Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-14 Manuscript/figs/experiments/sec4-experiments.tex
update

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}}
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
    \label{fig:exp_sampling_batch_train_time}
\end{figure}
\label{sec:effects_of_sampling_techniques_on_performance}

>>>>

\begin{figure}
    \centering
    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}}
    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
    \label{fig:exp_sampling_batch_train_time}
\end{figure}
\label{sec:effects_of_sampling_techniques_on_performance}
